---
title: "Measuring Naturalistic Speech Comprehension in Real Time Exp 2"
output: html_document

---
# DATA WRANGLING

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
# Load libraries

library(stringr)
library(fs)
library(readxl)
library(readr)
library(simr)
library(lmerTest)
library(patchwork)
library(RColorBrewer)
library(cowplot)
library(scales)
library(gridExtra)
library(PerformanceAnalytics)
library(corrplot)
library(Hmisc)
library(GGally)
library(visreg)
library(broom.mixed)
library(sjPlot)
library(gridExtra)
library(grid) 
library(rempsyc)
library(flextable)
library(officer)
library(ggsignif)
library(MuMIn)
library(rstatix)
library(caret)
library(modelr)
library(tidyr)
library(purrr)
library(broom)
library(dplyr)
library(ggplot2)
library(rsample)
library(emmeans)
library(readr)
library(stringr)


# set the default ggplot theme 
theme_set(theme_classic())
```

```{r}
# Set path and participant ids

# Change the folder path to data folder relative to the wd
folder_path <- '/Users/irmakergin/Desktop/experiment_2/data/raw_data'

# Define the list of participant IDs
participant_ids <- c("p_1","p_2","p_3","p_4","p_5","p_6","p_7","p_8","p_9",
                     "p_10","p_11","p_12","p_13","p_14","p_15","p_16","p_17",
                     "p_18","p_19","p_20","p_21","p_22","p_23","p_24","p_25",
                     "p_26","p_27","p_28","p_29","p_30")
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Organize the data csv files

# Get a list of all files in the folder
files <- dir(folder_path, full.names = TRUE)

# Set a path to save the organized files
organized_data_path <- "/Users/irmakergin/Desktop/experiment_2/data/organized_data"

# Find files by participant ID 
for(part_id in participant_ids) {
  
  slider_pattern <- paste0("^slider_", part_id, "(?:[_\\.-]|$).*\\.csv$")
  additional_csv_pattern <- paste0("^", part_id, "(?:[_\\.-]|$).*\\.csv$")

  # Find slider files that match the pattern
  slider_matched_files <- files[str_detect(basename(files), slider_pattern)]
  
  # Find data CSV files that match the pattern
  additional_csv_matched_files <- files[str_detect(basename(files), additional_csv_pattern)]
  
  # Create a directory for the current participant on the organized data path
  participant_folder <- file.path(organized_data_path, part_id)
  if(!dir.exists(participant_folder)) {
    dir.create(participant_folder, recursive = TRUE, showWarnings = TRUE)
  }
  
  # Create a subdirectory for slider files within the participant folder
  slider_folder <- file.path(participant_folder, paste0("slider_", part_id))
  if(!dir.exists(slider_folder)) {
    dir.create(slider_folder, recursive = TRUE, showWarnings = TRUE)
  }
  
  # Move slider matched files to the slider subfolder
  if(length(slider_matched_files) > 0) {
    for(file in slider_matched_files) {
      file_copy(file, file.path(slider_folder, basename(file)), overwrite = TRUE)
    }
  }
  
  # Move additional CSV matched files (experiment data) to the main participant folder 
  # and rename the participant folders
  if(length(additional_csv_matched_files) > 0) {
    for(file in additional_csv_matched_files) {
      new_name <- paste0(part_id, "_raw_data.csv")
      file_copy(file, file.path(participant_folder, new_name), overwrite = TRUE)
    }
  }
  
  # Status check
  if(length(slider_matched_files) > 0 || length(additional_csv_matched_files) > 0) {
    cat("Files for participant ID '", part_id, 
        "' have been organized successfully. Slider files in: ", slider_folder, 
        ", other CSVs in: ", participant_folder, "\n")
  } else {
    cat("No files found for participant ID '", part_id, "'.\n")
  }
}

# Loop through each participant ID
for (part_id in participant_ids) {
  # Define the path to the participant's raw data CSV
  raw_data_path <- file.path(organized_data_path, 
                             part_id, 
                             paste0(part_id, "_raw_data.csv"))
  
  # Read and process the CSV for each participant
  if (file.exists(raw_data_path)) {
    
    df.raw <- read_csv(raw_data_path) %>%
      filter(!wav_file %in% c("Someday_trial_condition.wav", 
                              "Someday_trial_condition-5x.wav")) %>%
      mutate(index = row_number()) %>%
      select(index, participant, wav_file, duration) %>%
      group_by(wav_file) %>%
      summarise(
        index = first(index), 
        participant = first(participant), 
        duration = first(duration),
        .groups = 'drop'
      ) %>%
      arrange(index) %>%
      slice(-1) %>%  # Remove the first row
      mutate(index = row_number()) %>%  # Recalculate index after row removal
      rename(
        overall_duration = duration,
        part_wav_merged = wav_file
      )
    
    # Save to global environment with participant-specific name
    assign(paste0("df.raw.merged_", part_id), df.raw, envir = .GlobalEnv)
    
    # Remove temporary variable
    rm(df.raw)
  }
}
```

```{r}
meta_part1 <- read_excel("/Users/irmakergin/Desktop/experiment_2/someday_continuous_spedup_part1.xlsx") %>%
  mutate(part = 1)

meta_part2 <- read_excel("/Users/irmakergin/Desktop/experiment_2/someday_continuous_spedup_part2.xlsx") %>%
  mutate(part = 2)

meta_combined <- bind_rows(meta_part1, meta_part2) %>%
  rename(
    wav_index = index,
    wav_name = file,
    speech_rate = condition
  ) %>%
  select(wav_index, wav_name, speech_rate, part)

m_rows <- nrow(meta_combined) 

for (part_id in participant_ids) {
  local({
    df_name <- paste0("df.raw.merged_", part_id)
    
    if (exists(df_name, envir = .GlobalEnv)) {
      df <- get(df_name, envir = .GlobalEnv)
      n_rows <- nrow(df)
      repeat_factor <- ceiling(m_rows / n_rows)
      df_expanded <- df[rep(1:n_rows, times = repeat_factor), ]
      df_expanded <- df_expanded[1:m_rows, ]
      df_expanded$index <- seq_len(m_rows)

      df_extended <- bind_cols(df_expanded, meta_combined)
      df_extended$part_wav_merged <- ifelse(
        df_extended$part == 1,
        "someday_continuous_spedup_part1.wav",
        "someday_continuous_spedup_part2.wav"
      )
      df_extended <- df_extended %>%
        select(-part_wav_merged, everything(), part_wav_merged)

      assign(df_name, df_extended, envir = .GlobalEnv)
      cat("✓ Updated", df_name, "\n")
    } else {
      warning("No dataframe found for participant ID:", part_id)
    }
  })
}
```
Merge conditions
```{r}
for (part_id in participant_ids) {
  local({
    df_name <- paste0("df.raw.merged_", part_id)
    
    if (exists(df_name, envir = .GlobalEnv)) {
      df <- get(df_name, envir = .GlobalEnv)
      
      # Create a run ID for each consecutive group of same speech_rate
      rle_result <- rle(df$speech_rate)
      run_ids <- rep(seq_along(rle_result$lengths), rle_result$lengths)
      df$run_id <- run_ids
      
      # Group by run_id only (not speech_rate), since we want to keep consecutive structure
      df_grouped <- df %>%
        group_by(run_id) %>%
        summarise(
          index = first(index),  # will be reassigned below anyway
          participant = first(participant),
          overall_duration = first(overall_duration),
          wav_index = paste(wav_index, collapse = ","),
          wav_name = paste(wav_name, collapse = ","),
          speech_rate = first(speech_rate),
          part = first(part),
          part_wav_merged = first(part_wav_merged),
          .groups = "drop"
        ) %>%
        mutate(index = row_number()) %>%
        select(index, participant, overall_duration, wav_index, wav_name,
               speech_rate, part, part_wav_merged)
      
      # Save updated dataframe
      assign(df_name, df_grouped, envir = .GlobalEnv)
      cat("✓ Grouped df.raw.merged_", part_id, " → ", nrow(df_grouped), " rows\n", sep = "")
    }
  })
}
```

Add  Digit Span scores
```{r}
for (part_id in participant_ids) {
  local({
    df_name <- paste0("df.raw.merged_", part_id)
    digit_path <- file.path("/Users/irmakergin/Desktop/experiment_2/data/organized_data", 
                            paste0("digit_span_", part_id, ".xlsx"))
    
    if (exists(df_name, envir = .GlobalEnv) && file.exists(digit_path)) {
      df <- get(df_name, envir = .GlobalEnv)
      
      # Read the digit span file and extract score
      digit_df <- readxl::read_excel(digit_path)
      score_value <- digit_df$score[1]  # assumes score is in first row
      
      # Add score to all rows
      df$digit_span_score <- score_value
      
      # Save updated dataframe
      assign(df_name, df, envir = .GlobalEnv)
      cat("✓ Added digit span score for", part_id, "\n")
    } else {
      warning("Missing dataframe or digit span file for participant:", part_id)
    }
  })
}
```
Add hearWHO scores

```{r}
# Load hearWHO scores once
hearwho_path <- "/Users/irmakergin/Desktop/experiment_2/data/organized_data/hearwho_scores.xlsx"
hearwho_df <- readxl::read_excel(hearwho_path)

for (part_id in participant_ids) {
  local({
    df_name <- paste0("df.raw.merged_", part_id)
    
    if (exists(df_name, envir = .GlobalEnv)) {
      df <- get(df_name, envir = .GlobalEnv)
      
      # Match participant row in hearWHO score sheet
      match_row <- hearwho_df %>% filter(participant == part_id)
      
      if (nrow(match_row) == 1) {
        score_value <- match_row$score[1]
        df$digit_in_noise_score <- score_value
        assign(df_name, df, envir = .GlobalEnv)
        cat("✓ Added hearing score for", part_id, "\n")
      } else {
        warning("Could not find a unique hearing score for participant:", part_id)
      }
    } else {
      warning("No dataframe found for participant:", part_id)
    }
  })
}
```
Add slider values
every condition except 1x is 7.55000 s long, 1x is 7.5000 s 
```{r}


# Function to split slider stream into exact time chunks based on trial durations
split_slider_by_speech_rate <- function(slider_df, trial_df) {
  slider_df <- slider_df %>% 
    rename(time_ms = time, value = value) %>% 
    mutate(time = time_ms / 1000)  # convert ms to sec
  
  result <- vector("list", nrow(trial_df))
  current_time <- 0
  for (i in seq_len(nrow(trial_df))) {
    rate <- trial_df$speech_rate[i]
    duration <- ifelse(rate == 1, 7.5, 7.55)
    
    # Slice from slider stream based on cumulative time window
    trial_slice <- slider_df %>%
      filter(time >= current_time & time < current_time + duration)
    
    # Save chunk
    result[[i]] <- tibble(
      slider_values = paste0("[", paste(trial_slice$value, collapse = ", "), "]"),
      slider_times  = paste0("[", paste(trial_slice$time, collapse = ", "), "]")
    )
    
    current_time <- current_time + duration
  }

  bind_rows(result)
}

# Loop over all participants and process their slider data
for (part_id in participant_ids) {
  local({
    df_name <- paste0("df.raw.merged_", part_id)
    
    if (!exists(df_name, envir = .GlobalEnv)) {
      warning("Missing merged dataframe for ", part_id)
      return()
    }
    
    df <- get(df_name, envir = .GlobalEnv)
    
    slider_dir <- file.path(organized_data_path, part_id, paste0("slider_", part_id))
    slider_file1 <- list.files(slider_dir, pattern = "part1.*\\.csv$", full.names = TRUE)
    slider_file2 <- list.files(slider_dir, pattern = "part2.*\\.csv$", full.names = TRUE)
    
    read_slider <- function(file) {
      if (length(file) == 0) return(NULL)
      df <- readr::read_csv(file, skip = 1, show_col_types = FALSE)
      if (!all(c("value", "time") %in% names(df))) return(NULL)
      return(df)
    }
    
    s1 <- read_slider(slider_file1)
    s2 <- read_slider(slider_file2)
    
    if (is.null(s1) || is.null(s2)) {
      warning("Missing or malformed slider files for ", part_id)
      return()
    }
    
    # Split df into part1 and part2 trials
    df1 <- df[1:80, ]
    df2 <- df[81:160, ]
    
    # Assign slider chunks based on cumulative time windows per trial
    chunks1 <- split_slider_by_speech_rate(s1, df1)
    chunks2 <- split_slider_by_speech_rate(s2, df2)
    
    # Combine chunks
    slider_combined <- bind_rows(chunks1, chunks2)
    
    if (nrow(slider_combined) != nrow(df)) {
      warning("Slider chunk mismatch for ", part_id)
    }
    
    df$slider_values <- slider_combined$slider_values
    df$slider_times  <- slider_combined$slider_times
    
    assign(df_name, df, envir = .GlobalEnv)
    cat("✓ Updated", df_name, "with time-based slider chunks\n")
  })
}


```


Rescale slider values to be between 0 and 1 
```{r}
for (part_id in participant_ids) {
  local({
    df_name <- paste0("df.raw.merged_", part_id)
    
    if (exists(df_name, envir = .GlobalEnv)) {
      df <- get(df_name, envir = .GlobalEnv)

      # Step 1: Parse slider_values from string to list of numeric vectors
      df$slider_values <- strsplit(as.character(df$slider_values), ",\\s*|\\[|\\]")
      df$slider_values <- lapply(df$slider_values, function(x) {
        x <- x[nzchar(x)]  # remove empty strings
        as.numeric(x)
      })

      # Step 2: Define rescaling function
      rescale_values <- function(values) {
        sapply(values, function(x) x / 255)
      }

      # Step 3: Apply rescaling
      df$slider_values_rescaled <- lapply(df$slider_values, rescale_values)

      # Save back to environment
      assign(df_name, df, envir = .GlobalEnv)
      cat("✓ Rescaled slider values for", df_name, "\n")
    }
  })
}
```

merge all participant files into one
```{r}
# Get all participant merged dataframes
participant_dfs <- mget(ls(pattern = "^df\\.raw\\.merged_"))

# Combine all into one dataframe
df.raw <- bind_rows(participant_dfs, .id = "source")

# Extract participant ID from source column and create a proper 'participant' column
df.raw <- df.raw %>%
  mutate(participant = gsub("df\\.raw\\.merged_", "", source)) %>%
  select(-source)

```

Add duration of each column

```{r}

# Step 1: Compute durations
df.raw <- df.raw %>%
  mutate(
    slider_times = as.character(slider_times),
    duration = map_dbl(slider_times, function(times_str) {
      if (is.na(times_str) || times_str == "[]") return(NA_real_)
      
      times <- as.numeric(unlist(strsplit(gsub("\\[|\\]", "", times_str), ",\\s*")))
      if (length(times) < 2 || anyNA(times)) return(NA_real_)
      
      max(times) - min(times)
    })
  )

# Step 2: Summary
summary(df.raw$duration)

# Step 3: Get rows with min and max durations
min_row <- df.raw %>% filter(duration == min(duration, na.rm = TRUE))
max_row <- df.raw %>% filter(duration == max(duration, na.rm = TRUE))

# Step 4: Print full row info, including slider_times
cat("\n--- Row with MIN duration ---\n")
print(min_row %>% select(everything(), slider_times))

cat("\n--- slider_times for MIN duration row ---\n")
cat(min_row$slider_times, "\n")

cat("\n--- Row with MAX duration ---\n")
print(max_row %>% select(everything(), slider_times))

cat("\n--- slider_times for MAX duration row ---\n")
cat(max_row$slider_times, "\n")


```

```{r}
# Save merged dataframe for slider visualizations
# Make a copy first so we don't modify df.raw directly
df.export <- df.raw

# Convert list columns to character strings (if they are lists)
list_cols <- sapply(df.export, is.list)

df.export[list_cols] <- lapply(df.export[list_cols], function(col) {
  sapply(col, function(x) paste(x, collapse = ","))
})

# Write to CSV
write.csv(df.export, file = "/Users/irmakergin/Desktop/experiment_2/data/organized_data/df.raw.csv", row.names = FALSE)

```

## Exclusion Criteria 
###  Slider movements
For the physical slider to ensure that participants actually used it actively: Distribution of the amount of slider movements across trials and participants- If a participant's slider movements exceeds ±3.5 standard deviations from the mean, we will remove those participants' data.


```{r}
# Calculate movement score with magnitude for each trial
df.raw <- df.raw %>%
  rowwise() %>%
  mutate(trial_movement_score_magnitude = sum(abs(diff(unlist(slider_values))))) %>%
  ungroup()

# Aggregate these scores for each participant
participant_movement_scores <- df.raw %>%
  group_by(participant) %>%
  summarise(movement_score_all = sum(trial_movement_score_magnitude, na.rm = TRUE))

# Add the movement scores back to the df
df.raw <- left_join(df.raw, participant_movement_scores, by = "participant")

# Calculate mean and standard deviation for movement scores, identify outliers
mean_movement_score <- mean(participant_movement_scores$movement_score_all, na.rm = TRUE)
sd_movement_score <- sd(participant_movement_scores$movement_score_all, na.rm = TRUE)

cutoff_upper <- mean_movement_score + 3.5 * sd_movement_score
cutoff_lower <- mean_movement_score - 3.5 * sd_movement_score

outliers <- participant_movement_scores %>%
  filter(movement_score_all < cutoff_lower | movement_score_all > cutoff_upper) %>%
  pull(participant)

# Print participant IDs for those outside the ±3.5 SD range
cat("Participants outside the ±3.5 SD range:", paste(outliers, collapse = ", "), "\n")
```
# ANALYSIS

## Do median slider responses for each speech rate significantly different than each other?

First let's get mean slider responses per trial
```{r}
df.data <- df.raw %>%
  ungroup() %>%  
  mutate(
    trial_mean_rescaled   = map_dbl(slider_values_rescaled, ~ mean(.x, na.rm = TRUE)),
    trial_median_rescaled = map_dbl(slider_values_rescaled, ~ median(.x, na.rm = TRUE))
  )

```

Does speech_rate have a significant effect on slider responses overall?


```{r}
m_rate <- lmer(
  trial_median_rescaled ~ speech_rate +
    (1 | digit_span_score) + (1 | digit_in_noise_score),
  data = df.data
)
summary(m_rate) #Estimates for each level of sr vs x1
#anova(m_rate) is this useful:
# Does including speech_rate as a predictor significantly improve the model fit compared to a model with just the intercept and random effects?

#pairwise comparisons
emm <- emmeans(m_rate, ~ speech_rate)
pairs(emm, adjust = "tukey")  
```

```{r}
pwpp(emm, adjust = "tukey") +
  labs(title = "Pairwise comparisons (Tukey-adjusted p-values)")

# model-estimated marginal means (EMMs) for each speech rate — i.e., the mean of 
# outcome predicted by the model
```

```{r}
# --- EMMs and CIs for bar heights ---
emm    <- emmeans(m_rate, ~ speech_rate)
emm_ci <- as.data.frame(confint(emm))

# robust CI colnames
nm <- names(emm_ci)
lower_col <- intersect(c("lower.CL","asymp.LCL","LCL"), nm)[1]
upper_col <- intersect(c("upper.CL","asymp.UCL","UCL"), nm)[1]

bar_df <- emm_ci %>%
  rename(lower = all_of(lower_col), upper = all_of(upper_col)) %>%
  mutate(
    rate_num = readr::parse_number(as.character(speech_rate))
  ) %>%
  arrange(rate_num) %>%
  mutate(
    speech_rate = factor(as.character(speech_rate),
                         levels = as.character(speech_rate))
  )

# --- Tukey pairs (parse numeric labels!) ---
pairs_df <- as.data.frame(pairs(emm, adjust = "tukey")) %>%
  separate(contrast, c("group1","group2"), sep = " - ", remove = TRUE) %>%
  mutate(
    g1_num = readr::parse_number(group1),
    g2_num = readr::parse_number(group2),
    stars  = case_when(
      p.value < .001 ~ "***",
      p.value < .01  ~ "**",
      p.value < .05  ~ "*",
      TRUE           ~ "ns"
    )
  )

# keep only significant (or comment this line to show all)
pairs_df <- filter(pairs_df, stars != "ns")

# map to x positions using the numeric value
lvl_nums <- bar_df$rate_num
pairs_df <- pairs_df %>%
  mutate(
    x1 = match(g1_num, lvl_nums),
    x2 = match(g2_num, lvl_nums)
  ) %>%
  drop_na(x1, x2) %>%         # drop any residual mismatches
  arrange(x1, x2)

# --- y positions with plenty of headroom ---
yrng <- range(c(bar_df$lower, bar_df$upper), na.rm = TRUE)
span <- diff(yrng)
if (!is.finite(span) || span == 0) span <- max(bar_df$emmean, na.rm = TRUE)

step  <- 0.08 * span                              # vertical spacing between brackets
basey <- max(bar_df$upper, na.rm = TRUE) + 0.04*span

ann <- pairs_df %>%
  mutate(
    layer = row_number(),
    y     = pmax(bar_df$upper[x1], bar_df$upper[x2]) + 0.02*span + step*(layer - 1)
  )

# --- Plot: bars + CI + manual brackets + asterisks ---
ggplot(bar_df, aes(x = speech_rate, y = emmean)) +
  geom_col(width = 0.8, fill = "grey70", color = "grey30") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.08, linewidth = 0.6) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.60))) +  # headroom for many brackets
  coord_cartesian(clip = "off") +
  # bracket horizontals
  geom_segment(data = ann, aes(x = x1, xend = x2, y = y, yend = y),
               linewidth = 0.6, inherit.aes = FALSE) +
  # bracket vertical ticks
  geom_segment(data = ann, aes(x = x1, xend = x1, y = y, yend = y - 0.12*step),
               linewidth = 0.6, inherit.aes = FALSE) +
  geom_segment(data = ann, aes(x = x2, xend = x2, y = y, yend = y - 0.12*step),
               linewidth = 0.6, inherit.aes = FALSE) +
  # asterisks
  geom_text(data = ann, aes(x = (x1 + x2)/2, y = y + 0.12*step, label = stars),
            size = 4, inherit.aes = FALSE) +
  labs(x = "Speech rate", y = "Median slider (EMM ± 95% CI)",
       title = "Estimated marginal means by speech rate",
       subtitle = "Brackets show Tukey-adjusted pairwise tests (* p<.05, ** p<.01, *** p<.001)") +
  theme_classic(base_size = 13)



```

```{r}
plot(emm)   # plot  EMMs with 95% CIs

```
## Is there a difference between dominant vs non-dominant hand?
We asked people to use their left hand during the first half and right hand
during the second half
```{r}
df.hand <- df.data %>%
  group_by(speech_rate, part) %>%
  summarise(
    mean_median = mean(trial_median_rescaled, na.rm = TRUE),
    se = sd(trial_median_rescaled, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  )

ggplot(
  df.hand %>% mutate(part = factor(part, levels = c(1, 2), 
                                   labels = c("Left","Right"))),
  aes(x = factor(speech_rate), y = mean_median, fill = part)
) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  geom_errorbar(
    aes(ymin = mean_median - se, ymax = mean_median + se),
    width = 0.2, position = position_dodge(width = 0.9)
  ) +
  scale_y_continuous(
    limits = c(0, 1),
    breaks = seq(0, 1, 0.25),
    labels = sprintf("%.2f", seq(0, 1, 0.25)),
    expand = c(0, 0)    # removes the gap below 0
  ) +
  scale_fill_manual(
    name = "Hand used",
    values = c("Left" = "#FFC0CB",  # baby pink
               "Right" = "#F2A337") # baby blue
  ) +
  labs(x = "Speech Rate", y = "Mean of Median Slider Response")
```


```{r}
m_part <- lmer(
  trial_median_rescaled ~ speech_rate * part +
    (1|digit_span_score) + (1|digit_in_noise_score),
  data = df.data
)
summary (m_part)
```

Compare models with(out) fixed effects and interaction
```{r}
anova(m_part)   # omnibus test
```
So the median slider responses change with speech rate but not with the hand\
used, and there is no interaction between the two.
