---
title: "Measuring Naturalistic Speech Comprehension in Real Time Supplamentary"
output: html_document

---
Analysis on participants eliminated from exp1 due to failing the preregistered
attention checks/ criteria

# DATA WRANGLING

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
# Load libraries

library(stringr)
library(fs)
library(readxl)
library(readr)
library(simr)
library(lmerTest)
library(patchwork)
library(RColorBrewer)
library(cowplot)
library(scales)
library(gridExtra)
library(PerformanceAnalytics)
library(corrplot)
library(Hmisc)
library(GGally)
library(visreg)
library(broom.mixed)
library(sjPlot)
library(gridExtra)
library(grid) 
library(rempsyc)
library(flextable)
library(officer)
library(ggsignif)
library(MuMIn)
library(rstatix)
library(caret)
library(modelr)
library(tidyr)
library(purrr)
library(broom)
library(dplyr)
library(ggplot2)
library(rsample)
library(emmeans)
library(readr)
library(stringr)
library(partR2)
library(multcomp)



# set the default ggplot theme 
theme_set(theme_classic())
```

```{r}
# Set path and participant ids

# Change the folder path to data folder relative to the wd
folder_path <- '/Users/irmakergin/Desktop/supplamentary/data'

# Define the list of participant IDs
participant_ids <- c("p_2","p_6","p_12","p_16","p_20","p_23","p_26","p_27")
```

```{r}
# upload data after semantic similarity calculations
df.data <- read.csv(file.path(folder_path, "df_semantic.csv"))
```

```{r}
# Calculate median trial movements for each trial

df.data <- df.data %>%
  mutate(
    slider_values_numeric = str_split(slider_values_rescaled, ",") %>%
      map(~ as.numeric(.x))
  )

# Mean and median slider values for each trial
df.data <- df.data %>%
  rowwise() %>%
  mutate(trial_mean_rescaled = mean(unlist(slider_values_numeric), na.rm = TRUE),
         trial_median_rescaled = median(unlist(slider_values_numeric), na.rm = TRUE)) %>%
  ungroup()
```

# EXCLUDED PARTICIPANTS 

## I. Semantic Similarity

### How many words did excluded participants write in their summaries on average?

```{r}
# on average, across speech rates
df.data <- df.data %>%
  mutate(
    summary_text = textbox.text_corrected_manual,
    summary_text = ifelse(is.na(summary_text), "", summary_text),
    summary_text = stringr::str_squish(summary_text),
    word_count   = ifelse(summary_text == "", NA_integer_,
                          stringr::str_count(summary_text, "\\S+"))
  )
overall_avg <- df.data %>%
  summarise(
    mean_words = round(mean(word_count, na.rm = TRUE),2),
    n_summaries = round(sum(!is.na(word_count)),2),
    total_words = round(sum(word_count, na.rm = TRUE),2)
  )

overall_avg
```

```{r}
# on average, per speech rate
by_rate <- df.data %>%
  group_by(speech_rate) %>%
  summarise(
    mean_words = round(mean(word_count, na.rm = TRUE),2),
    sd_words   = round(sd(word_count, na.rm = TRUE),2),
    n_summaries = round(sum(!is.na(word_count)),2),
    total_words = round(sum(word_count, na.rm = TRUE),2),
    .groups = "drop"
  ) %>%
  arrange(suppressWarnings(as.numeric(as.character(speech_rate))))

by_rate
```

Which semantic similarity analysis explains comprehension better?

### Visualization
First, let's visualize all 3 to see if they show the same pattern:

```{r figure-size, fig.width=9, fig.height=5}

# GloVe - Written Summary
average_similarity_summary <- df.data %>%
  group_by(speech_rate) %>%
  summarise(
    average_similarity = mean(glove_sum_max_similarity_rescaled, na.rm = TRUE),
    sd = sd(glove_sum_max_similarity_rescaled, na.rm = TRUE),
    n = n(),
    se = sd / sqrt(n)  # standard error
  )


# GloVe - Heard Segment
average_similarity_text <- df.data %>%
  group_by(speech_rate) %>%
  summarise(
    average_similarity = mean(glove_text_average_max_similarity, na.rm = TRUE),
    sd = sd(glove_text_average_max_similarity, na.rm = TRUE),
    n = n(),
    se = sd / sqrt(n)  # standard error
  )

# BERT 
average_similarity_bert <- df.data %>%
  group_by(speech_rate) %>%
  summarise(
    average_similarity = mean(bert_cosine_similarity, na.rm = TRUE),
    sd = sd(bert_cosine_similarity, na.rm = TRUE),
    n = n(),
    se = sd / sqrt(n)  # standard error
  )


# Create the plots without x and y labels
plot_glove_summary <- ggplot(average_similarity_summary, aes(x = factor(speech_rate), 
                               y = average_similarity, 
                               fill = as.factor(speech_rate))) +
  geom_bar(stat = "identity", position = "dodge", width = 0.7, fill = "green3") +
  scale_x_discrete(labels = function(x) paste0("x ", x)) +
  labs(x = NULL, y= NULL, 
       title = "GloVe- Written Summary") +
  geom_text(aes(label = round(average_similarity, 2)), 
            vjust = -1, position = position_dodge(width = 0.7), size = 3) +
  geom_errorbar(aes(ymin = average_similarity - se, ymax = average_similarity + se), 
                width = 0, position = position_dodge(width = 0.7)) + 
  theme(axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        plot.title = element_text(size = 13, hjust = 0.5))

plot_glove_text <- ggplot(average_similarity_text, aes(x = factor(speech_rate), 
                               y = average_similarity, 
                               fill = as.factor(speech_rate))) +
  geom_bar(stat = "identity", position = "dodge", width = 0.7, fill = "darkseagreen2") +
  scale_x_discrete(labels = function(x) paste0("x ", x)) +
  labs(x = NULL, y = NULL, 
       title = "GloVe - Heard Segment") +
  geom_text(aes(label = round(average_similarity, 2)), 
            vjust = -1, position = position_dodge(width = 0.7), size = 3) +
  geom_errorbar(aes(ymin = average_similarity - se, ymax = average_similarity + se), 
                width = 0,position = position_dodge(width = 0.7)) +
  theme(plot.title = element_text(size = 13, hjust = 0.5))

# Adjust the plot for BERT without individual axis labels
plot_bert <- ggplot(average_similarity_bert, aes(x = factor(speech_rate), 
                               y = average_similarity, 
                               fill = as.factor(speech_rate))) +
  geom_bar(stat = "identity", position = "dodge", width = 0.7, fill = "darkseagreen3") +
  scale_x_discrete(labels = function(x) paste0("x ", x)) +
  labs(x = NULL, y = NULL, 
       title = "BERT") +
  geom_text(aes(label = round(average_similarity, 2)), 
            vjust = -1.2, position = position_dodge(width = 0.7), size = 3) +
  geom_errorbar(aes(ymin = average_similarity - se, ymax = average_similarity + se), 
                width = 0, position = position_dodge(width = 0.7)) +
  theme(plot.title = element_text(size = 13, hjust = 0.5))

#put them in a grid 
grid.arrange(
  arrangeGrob(
  plot_glove_summary,plot_glove_text, plot_bert, 
    ncol = 3,
    left = textGrob("Average Normalized Cosine Similarity Value", 
                    rot = 90, vjust = 0.5),
   bottom = textGrob("Speech Rate", 
                    rot = 0, vjust = 0.5)
  ) 
)
```
### Correlation

Do 3 different semantic similarity measures correlate with each other?
```{r}
# Subset the relevant columns
semantic_columns <- df.data[, c("bert_cosine_similarity", 
                                "glove_text_average_max_similarity", 
                                "glove_sum_max_similarity_rescaled")]

# Calculate the correlation matrix
correlation_matrix <- cor(semantic_columns, use = "complete.obs")

# Print 
print(correlation_matrix)

```
Test if any of these correlations are statistically significant:
```{r}
# Correlation test between BERT and GloVe- Heard Segment
test1 <- cor.test(df.data$bert_cosine_similarity, 
                  df.data$glove_text_average_max_similarity)

# Correlation test between BERT and GloVe- Written Summary
test2 <- cor.test(df.data$bert_cosine_similarity, 
                  df.data$glove_sum_max_similarity_rescaled)

# Correlation test between GloVe- Heard Segment & GloVe- Written Summary
test3 <- cor.test(df.data$glove_text_average_max_similarity,
                  df.data$glove_sum_max_similarity_rescaled)

print(test1)
print(test2)
print(test3)

```

### Comparison
Which semantic similarity analysis method explains the most varience in comprehension?

To see which if  semantic similarity scores explains variance in comprehension better than the others,we conducted a linear mixed model was conducted to predict the 10-Point Scale responses based on BERT, GloVe- Written Summary, and GloVe- Heard Segment. Random effects for digit span score and digit in noise score were included in the model.


```{r}
# We first need to change the type of likert scale responses
# Fix decimal separator first
df.data$likert_rescaled <- gsub(",", ".", df.data$likert_rescaled)

# Now safely convert to numeric
df.data$likert_rescaled <- as.numeric(df.data$likert_rescaled)

# Check result
summary(df.data$likert_rescaled)
str(df.data$likert_rescaled)

```

```{r}
df.data$likert_rescaled <- as.numeric(as.character(df.data$likert_rescaled))

```


```{r}
model_all<- lmer(likert_rescaled ~ 
                 bert_cosine_similarity +   glove_text_average_max_similarity +   
                   glove_sum_max_similarity_rescaled + 
                (1 | digit_span_score) + 
                (1 | digit_in_noise_score), data = df.data)
#model_compare <- anova(model_g1, model_all)
summary(model_all) 
```
All fixed effects (different sem similarity scores) are significant but GloVe- Heard Segment.For the The other two are finding independent variance. For the participant who did not fail the inclusion criteria all 3 were significant. But as for included participants, Glove- Written Summary has the highest t value and estimate. Therefore, I will use/ report the GLoVe- written summary Segment for the rest of the analyses.   

### Speech Rate 
Are semantic similarity scores btw speech rates sig different from each other?

#### Glove- Written Summary
```{r}
semantic.anova <- aov(glove_sum_max_similarity_rescaled ~ speech_rate, data = df.data)
summary(semantic.anova)

pairwise_results <- df.data %>% pairwise_t_test(
    glove_sum_max_similarity_rescaled ~ speech_rate, pool.sd = FALSE,
    p.adjust.method = "bonferroni"
    )
pairwise_results
```
all significant except x1-x2 & x2-x3
Included participants: All significant except x1-x2

#### Glove- Heard Segment
```{r}
semantic.anova2 <- aov(glove_text_average_max_similarity ~ speech_rate, data = df.data)
summary(semantic.anova2)

pairwise_results2 <- df.data %>% pairwise_t_test(
    glove_text_average_max_similarity ~ speech_rate, pool.sd = FALSE,
    p.adjust.method = "bonferroni"
    )
pairwise_results2
```
All significant except x1-x2, x1-x3, x2-x3, & x4-x5
Included participants: All significant except x1-x2 & x2-x3

#### BERT
```{r}
semantic.anova3 <- aov(bert_cosine_similarity ~ speech_rate, data = df.data)
summary(semantic.anova3)

pairwise_results3 <- df.data %>% pairwise_t_test(
    bert_cosine_similarity ~ speech_rate, pool.sd = FALSE,
    p.adjust.method = "bonferroni"
    )
pairwise_results3
```
All significant except except x1-x2
Included participants: All significant except except x2-x3

### Recency Effect
Is there a recency effect in summaries that participants wrote?

#### Glove- Written Summary
```{r}
# First, make sure that the right ones are NA, right now NAs are also 0
df.data <- df.data %>%
  mutate(
    rescaled_glove_bin1 = ifelse(textbox.text_corrected_manual == "", 
                                 NA, rescaled_glove_bin1),
    rescaled_glove_bin2 = ifelse(textbox.text_corrected_manual == "", 
                                 NA, rescaled_glove_bin2),
    rescaled_glove_bin3 = ifelse(textbox.text_corrected_manual == "", 
                                 NA, rescaled_glove_bin3),
    rescaled_glove_bin4 = ifelse(textbox.text_corrected_manual == "", 
                                 NA, rescaled_glove_bin4),
    rescaled_glove_bin5 = ifelse(textbox.text_corrected_manual == "", 
                                 NA, rescaled_glove_bin5)
  )

# Create a long dataset for bins and scores
df.bin <- df.data %>%
  select(participant, index, speech_rate, segment_text, textbox.text_corrected_manual, 
         glove_bin1, glove_bin2, glove_bin3, glove_bin4, glove_bin5) %>%
  pivot_longer(cols = starts_with("glove_bin"), 
               names_to = "bin", 
               names_prefix = "glove_bin", 
               values_to = "semantic_score") %>%
  mutate(bin = as.integer(bin)) %>%
  arrange(participant, index, bin)

# If a recency effect ->  latter bins should be recalled better than earlier ones
binned.anova <- aov(semantic_score ~ speech_rate * bin, data = df.bin)
summary(binned.anova)

df.bin_factor = df.bin %>%
  mutate(speech_bin = factor(paste(speech_rate, bin, sep="_")))

# pairwise comparison
df.bin_factor %>% pairwise_t_test(
   semantic_score ~ speech_bin, pool.sd = FALSE,
    p.adjust.method = "bonferroni"
    )
```

#### Glove- Heard Segment
```{r}
# First, make sure that the right ones are NA, right now NAs are also 0

df.data <- df.data %>%
  mutate(
    glove2_bin1 = ifelse(textbox.text_corrected_manual == "", NA, glove2_bin1),
    glove2_bin2 = ifelse(textbox.text_corrected_manual == "", NA, glove2_bin2),
    glove2_bin3 = ifelse(textbox.text_corrected_manual == "", NA, glove2_bin3),
    glove2_bin4 = ifelse(textbox.text_corrected_manual == "", NA, glove2_bin4),
    glove2_bin5 = ifelse(textbox.text_corrected_manual == "", NA, glove2_bin5)
  )

# Create a long dataset for bins and scores 
df.bin_glove2 <- df.data %>%
  select(participant, index, speech_rate, segment_text, textbox.text_corrected_manual, 
         glove2_bin1, glove2_bin2, glove2_bin3, glove2_bin4, glove2_bin5) %>%
  pivot_longer(cols = starts_with("glove2_bin"), 
               names_to = "bin", 
               names_prefix = "glove2_bin", 
               values_to = "glove2_score") %>%
  mutate(bin = as.integer(bin)) %>%
  arrange(participant, index, bin)

# If a recency effect ->  latter bins should be recalled better than earlier ones

binned.anova2 <- aov(glove2_score ~ speech_rate * bin, data = df.bin_glove2)
summary(binned.anova2)

df.bin_factor = df.bin_glove2 %>%
  mutate(speech_bin = factor(paste(speech_rate, bin, sep="_")))

# pairwise comparison
df.bin_factor %>% pairwise_t_test(
   glove2_score ~ speech_bin, pool.sd = FALSE,
    p.adjust.method = "bonferroni"
    )
```

#### BERT
```{r}
# Create a long dataset for bins and scores for BERT
df.bin_bert <- df.data %>%
  select(participant, index, speech_rate, segment_text, textbox.text_corrected_manual, 
         cosine_similarity_bin1, 
         cosine_similarity_bin2, 
         cosine_similarity_bin3, 
         cosine_similarity_bin4, 
         cosine_similarity_bin5) %>%
  pivot_longer(cols = starts_with("cosine_similarity_bin"), 
               names_to = "bin", 
               names_prefix = "cosine_similarity_bin", 
               values_to = "bert_score") %>%
  mutate(bin = as.integer(bin)) %>%
  arrange(participant, index, bin)

binned.anova_bert <- aov(bert_score ~ speech_rate * bin, data = df.bin_bert)
summary(binned.anova_bert)

df.bin_bert_factor = df.bin_bert %>%
  mutate(speech_bin = factor(paste(speech_rate, bin, sep="_")))

# pairwise comparison
df.bin_bert_factor %>% pairwise_t_test(
   bert_score ~ speech_bin, pool.sd = FALSE,
    p.adjust.method = "bonferroni"
    )
```
There is a main effect of Speech Rate for all 3, main effect of binning (recency) only for GloVe- Heard Segment & BERT as for the included participants. 

## II. Validation
Can we predict the scores of our novel comprehension measure from the existing post-hoc comprehension measures?

### Each measure as a fixed effect in seperate models

#### 10-Point Scale Ratings 

```{r}
model_likert<- lmer(trial_median_rescaled ~ 
                likert_rescaled + 
                (1 | digit_span_score) + 
                (1 | digit_in_noise_score), data = df.data)

summary(model_likert)
```

##### Visualize 10-Point Scale Ratings per Sepeech Speed
```{r figure-size, fig.width=6, fig.height=6 }

# Calculate the average 10-point scale scores per speech_rate category
average_score_likert <- df.data %>%
  group_by(speech_rate) %>%
  summarise(average_likert = mean(likert_rescaled, na.rm = TRUE),
            sd = sd(likert_rescaled, na.rm = TRUE),
            n = n(),
            se = sd / sqrt(n)  # standard error
  )

# Plot
likert_plot <- ggplot(average_score_likert, aes(x = factor(speech_rate), 
                                                y = average_likert)) +
  geom_bar(stat = "identity", width = 0.7, fill = "royalblue") +   
  labs(x = "Speech Rate", y = "10-Point Scale Response") +
  geom_text(aes(label = round(average_likert, 2)), vjust = -0.2, size = 6) +
  scale_x_discrete(labels = function(x) paste0("x ", x)) +
  geom_errorbar(aes(ymin = average_likert - se, ymax = average_likert + se), 
                width = 0, position = position_dodge(width = 0.5)) +  
  scale_y_continuous(breaks = c(0, 0.25, 0.50)) + 
  theme(axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24),
        axis.text.x = element_text(size = 20), 
        axis.text.y = element_text(size = 20))  

print(likert_plot)
```

#### Multiple Choice Quesitons
```{r}
model_multiple_choice<- lmer(trial_median_rescaled ~ 
                multiple_choice_accuracy + 
                (1 | digit_span_score) + 
                (1 | digit_in_noise_score), data = df.data)

summary(model_multiple_choice)
```

##### Visualize Multiple Choice Quesitons per Speech Rate
```{r figure-size, fig.width=6, fig.height=6 }
# Calculate the average multiple_choice_accuracy scores per speech_rate category
average_scores <- df.data %>%
  group_by(speech_rate) %>%
  summarise(average_accuracy = mean(multiple_choice_accuracy, na.rm = TRUE),
            sd = sd(multiple_choice_accuracy, na.rm = TRUE),
            n = n(),
            se = sd / sqrt(n)  # standard error
  )

question_plot <- ggplot(average_scores, aes(x = factor(speech_rate), y = average_accuracy)) +
  geom_bar(stat = "identity", width = 0.7, fill = "violetred") +   
  labs(x = "Speech Rate", y = "Multiple Choice Accuracy") +
  geom_text(aes(label = round(average_accuracy, 2)), vjust = -0.5, size = 6) +
  scale_x_discrete(labels = function(x) paste0("x ", x)) +
  geom_errorbar(aes(ymin = average_accuracy - se, ymax = average_accuracy + se), 
                width = 0, position = position_dodge(width = 0.5)) +
  # Add dashed line at chance level:
  geom_hline(yintercept = 0.25, linetype = "dashed", color = "black", size=1.5) +  
  scale_y_continuous(breaks = c(0, 0.25, 0.5)) +  
  theme(axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24),
        axis.text.x = element_text(size = 20),  
        axis.text.y = element_text(size = 20))  

print(question_plot)
```
Over chance performance in x5 speed despit reporting not understanding for
excluded participants as well

#### Summary
```{r}
# Summary- GloVe- Written Summary
model_glove1<- lmer(trial_median_rescaled ~ 
                glove_sum_max_similarity_rescaled + 
                (1 | digit_span_score) + 
                (1 | digit_in_noise_score), data = df.data)

summary(model_glove1)
```

##### Visualize Semantic Simlarity Scores of Summaries per Speech Rate
```{r figure-size, fig.width=6, fig.height=6}
plot_glove_summary <- ggplot(average_similarity_summary, aes(x = factor(speech_rate), 
                               y = average_similarity, 
                               fill = as.factor(speech_rate))) +
  geom_bar(stat = "identity", position = "dodge", width = 0.7, fill = "green3") +
  scale_x_discrete(labels = function(x) paste0("x ", x)) +
  labs(x = "Speech Rate", y= "Semantic Similarity\nScore") +
  geom_text(aes(label = round(average_similarity, 2)), 
            vjust = -0.5, position = position_dodge(width = 0.7), size = 6) +
  geom_errorbar(aes(ymin = average_similarity - se, ymax = average_similarity + se), 
                width = 0, position = position_dodge(width = 0.7)) + 
  scale_y_continuous(breaks = c(0, 0.25, 0.5), limits = c(0, 0.5)) +  
  theme(axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24),
        axis.text.x = element_text(size = 20),  
        axis.text.y = element_text(size = 20), 
        plot.title = element_text(size = 20, hjust = 0.5))

plot_glove_summary
```

### Visualize single fixed effect regression models
```{r figure-size, fig.width=6, fig.height=6 }
visreg_summary <- visreg(model_glove1, "glove_sum_max_similarity_rescaled", gg=TRUE,    
                         line=list(col="green3", size=1.7), points=list(alpha=0.5),
                         xlab= "Semantic Similarity Score", 
                         ylab= "Predicted Real-Time\nComprehension Score") +
  theme(axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24),
        axis.text.x = element_text(size = 20),  # Adjust X-axis tick label size
        axis.text.y = element_text(size = 20)) +  # Adjust Y-axis tick label size
  scale_x_continuous(breaks = c(0, 0.5, 1)) +  # Set x-axis ticks at 0, 0.5, 1
  scale_y_continuous(breaks = c(0, 0.5, 1)) 


visreg_likert <- visreg(model_likert, "likert_rescaled", gg=TRUE,
                        line=list(col="royalblue",size=1.7), points=list(alpha=0.5),
                        xlab= "10-point Scale Response", 
                        ylab= "") +
theme(axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24),
        axis.text.x = element_text(size = 20),  # Adjust X-axis tick label size
        axis.text.y = element_text(size = 20)) +  # Adjust Y-axis tick label size
  scale_x_continuous(breaks = c(0, 0.5, 1)) +  # Force x-axis to include 0, 0.5, 1
  scale_y_continuous(breaks = c(0, 0.5, 1))


visreg_multiple <- visreg(model_multiple_choice, "multiple_choice_accuracy", gg=TRUE,
                          line=list(col="violetred", size=1.7), points=list(alpha=0.5),
                          xlab= "Multiple Choice Accuracy", 
                          ylab= "") +
  theme(axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24),
        axis.text.x = element_text(size = 20),  # Adjust X-axis tick label size
        axis.text.y = element_text(size = 20)) +  # Adjust Y-axis tick label size
  scale_x_continuous(breaks = c(0, 0.5, 1)) +  # Set x-axis ticks at 0, 0.5, 1
  scale_y_continuous(breaks = c(0, 0.5, 1))


visreg_summary
visreg_likert
visreg_multiple
```

### Visualize regression models + Bar plots 
```{r figure-size, fig.width=18, fig.height=14}
# Create a multi-panel plot for 

# Create title groups
title1 <- textGrob("Summary", gp=gpar(fontsize=28, color='green3',fontface="bold"))
title2 <- textGrob("10-Point Scale", gp=gpar(fontsize=28, color='royalblue', fontface="bold"))
title3 <- textGrob("Multiple Choice Question", gp=gpar(fontsize=28,color='violetred', fontface="bold"))

combined_plot_effects <- grid.arrange(
  title1, title2, title3,
  visreg_summary, visreg_likert, visreg_multiple,
  plot_glove_summary, likert_plot, question_plot,
  ncol = 3,
  nrow = 4,
  heights = unit.c(unit(4, "null"), unit(8, "null"), unit(2, "null"), unit(8, "null")),  # Adjust heights
  layout_matrix = rbind(c(1, 2, 3), c(4, 5, 6), c(NA, NA, NA), c(7, 8, 9))
)

print(combined_plot_effects)
```

## All post-hoc measures as fixed effects in one regression model
Now predict the novel measure's scores from all post-hoc comprehension measures to see if they can explain independent variance.

```{r}
model_all_glove1 <- lmer(trial_median_rescaled ~  
                glove_sum_max_similarity_rescaled +
                likert_rescaled + 
                multiple_choice_accuracy + 
                (1 | digit_span_score) + 
                (1 | digit_in_noise_score), data = df.data)

summary(model_all_glove1)
```
Ah, unlike just included participants, when they are all included in the model 
only the liker scale is significant in predicting slider values- no
independently explained varinance

### Visualize the multiple fixed effects regression
```{r figure-size, fig.width=15, fig.height=5 }

visreg_summary_all <- visreg(model_all_glove1, "glove_sum_max_similarity_rescaled", 
                             gg=TRUE,
                          line=list(col="green3", size = 1.7), points=list(alpha=0.5),
                       xlab= "Semantic Similarity Score", 
                       ylab= "Predicted Real-Time\nComprehension Score") + 
  theme(axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24),
        axis.text.x = element_text(size = 20),  
        axis.text.y = element_text(size = 20)) +  
  scale_x_continuous(breaks = c(0, 0.5, 1)) +  
  scale_y_continuous(breaks = c(0, 0.5, 1))    

# Update for visreg_likert
visreg_likert_all <- visreg(model_all_glove1, "likert_rescaled", gg=TRUE,
                        line=list(col="royalblue",size=1.7), points=list(alpha=0.5),
                       xlab= "10-point Scale Response",
                       ylab= NULL)+ 
  theme(axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24),
        axis.text.x = element_text(size = 20),  
        axis.text.y = element_text(size = 20)) +  
  scale_x_continuous(breaks = c(0, 0.5, 1)) +  
  scale_y_continuous(breaks = c(0, 0.5, 1))    

# Update for visreg_multiple
visreg_multiple_all <- visreg(model_all_glove1, "multiple_choice_accuracy", gg=TRUE,
                           line=list(col="violetred", size=1.7), points=list(alpha=0.5),
                       xlab= "Multiple Choice Accuracy", 
                       ylab= NULL) +
  theme(axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24),
        axis.text.x = element_text(size = 20),  
        axis.text.y = element_text(size = 20)) +  
  scale_x_continuous(breaks = c(0, 0.5, 1)) +  
  scale_y_continuous(breaks = c(0, 0.5, 1))    

# Arrange plots in a grid
grid.arrange(
  arrangeGrob(
    visreg_summary_all, visreg_likert_all, visreg_multiple_all, 
    ncol = 3
  ) 
)


# For random slopes 
visreg_wm <- visreg(model_all_glove1, "digit_span_score", gg=TRUE,
                       xlab= "Working Memory Scores", 
                       ylab= NULL) 
  #scale_y_continuous(breaks = c(1, 2, 3, 4, 5), limits = c(1, 5))

visreg_hearing <- visreg(model_all_glove1, "digit_in_noise_score", gg=TRUE,
                       xlab= "Hearing In Noise", 
                       ylab= NULL)
  #scale_y_continuous(breaks = c(1, 2, 3, 4, 5), limits = c(1, 5))
  

# put them in a grid
grid.arrange(
  arrangeGrob(
   visreg_wm, visreg_hearing,
    ncol = 2,
    left = textGrob(" Predicted real-time comprehension scores 
                    given the post-hoc measures", 
                    rot = 90, vjust = 1.5)
  ) 
)
```

## Figure: Single fixed-effect regressions + bar plots + multiple fixed-effect regression
```{r figure-size, fig.width=18, fig.height=22}
# all 3 plots in the same grid
# Create title groups
title1 <- textGrob("Summary", gp=gpar(fontsize=28, 
                                      color='green3',
                                      fontface="bold"))
title2 <- textGrob("10-Point Scale", gp=gpar(fontsize=28, 
                                             color='royalblue', 
                                             fontface="bold"))
title3 <- textGrob("Multiple Choice Question", gp=gpar(fontsize=28,
                                                       color='violetred', 
                                                       fontface="bold"))

combined_plot_effects <- grid.arrange(
  title1, title2, title3,
  visreg_summary, visreg_likert, visreg_multiple,
  plot_glove_summary, likert_plot, question_plot,
  visreg_summary_all, visreg_likert_all, visreg_multiple_all,
  ncol = 3,
  nrow = 6,
  heights = unit.c(
    unit(4, "null"),  # Title row
    unit(8, "null"),  # First row of plots
    unit(2, "null"),  # Spacer row
    unit(8, "null"),  # Second row of plots
    unit(2, "null"),  # Spacer row (optional)
    unit(8, "null")   # Third row of plots
  ),
  layout_matrix = rbind(
    c(1, 2, 3),
    c(4, 5, 6),
    c(NA, NA, NA),
    c(7, 8, 9),
    c(NA, NA, NA),
    c(10, 11, 12)
  )
)


print(combined_plot_effects)
```
## Predicting real time comprehension from speech rate 
Does comprehension change with Speech Rate?

```{r}
model_rate <- lmer(speech_rate ~ 
                trial_median_rescaled +
                glove_sum_max_similarity_rescaled +
                likert_rescaled + 
                multiple_choice_accuracy + 
                (1 | digit_span_score) + 
                (1 | digit_in_noise_score), data = df.data)

summary(model_rate)
```

### Figure: Estimates of fixed effects (comprehension measures) on Speech Rate
```{r}
# Extract the fixed effects from the model (including confidence intervals)
fixed_effects <- tidy(model_rate, effects = "fixed", conf.int = TRUE)

# Filter out the intercept term
fixed_effects <- fixed_effects %>%
  filter(term != "(Intercept)")

# Map the actual terms to custom axis labels
term_mapping <- c(
  "multiple_choice_accuracy" = "Multiple Choice Question Accuracy",
  "glove_sum_max_similarity_rescaled" = "Summary Semantic Similarity",
  "likert_rescaled" = "10-Point Scale",
  "trial_median_rescaled" = "Median Real-Time Comprehension"
)

# Replace the term names with custom labels
fixed_effects <- fixed_effects %>%
  mutate(term = recode(term, !!!term_mapping))

# Reorder the terms based on the estimate values in descending order
fixed_effects <- fixed_effects %>%
  mutate(term = reorder(term, -estimate))

# Add a column for significance stars based on p-values
fixed_effects <- fixed_effects %>%
  mutate(sig_stars = case_when(
    p.value < 0.001 ~ "***",
    p.value < 0.01 ~ "**",
    p.value < 0.05 ~ "*",
    TRUE ~ ""
  ))

# Plot with ggplot2 - swapped x and y axes
ggplot(fixed_effects, aes(y = term, x = estimate)) +  # Swapped axes
  geom_point(aes(color = term), size = 3) +  # Add color to the points
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high, color = term), 
                 height = 0, 
                 width = 0) +  
  geom_text(aes(label = paste0(round(estimate, 2), sig_stars)), vjust = -1, size = 4) +  
  scale_color_manual(values = c(
    "Multiple Choice Question Accuracy" = "violetred",
    "10-Point Scale" = "royalblue",
    "Summary Semantic Similarity" = "green3",
    "Median Real-Time Comprehension" = "purple"
  )) + 
  labs(title = " ",
       x = "Regression Coefficient Estimates",
       y = NULL) +  
  theme(
    plot.title = element_text(hjust = 0.5, size = 18),  
    axis.title.x = element_text(size = 13),              
    axis.text.y = element_text(size = 13, color = "black"),  
    axis.text.x = element_text(size = 12) 
  ) + 
  guides(color = "none") 

```
Multiple choice accuracy is not significant anymore, unlike in just included participants

# ALL PARTICIPANTS (Excluded + Included)

First, load and merge excluded and included participant's data
```{r}
# excluded participants' data
df_exc <- read.csv("/Users/irmakergin/Desktop/supplamentary/data/df_semantic.csv")
# included participants' daha
df_inc <- read.csv("/Users/irmakergin/Desktop/supplamentary/data/df_semantic_included.csv")

# Check number of columns
if (ncol(df_exc) != ncol(df_inc)) {
  cat("Column number mismatch:\n",
      "df_exc has", ncol(df_exc), "columns, df_inc has", ncol(df_inc), "columns\n")
}

# Check column names
if (!identical(names(df_exc), names(df_inc))) {
  cat(" Column name mismatch:\n")
  cat("In df_exc not in df_inc:", setdiff(names(df_exc), names(df_inc)), "\n")
  cat("In df_inc not in df_exc:", setdiff(names(df_inc), names(df_exc)), "\n")
} else {
  cat("Column numbers and names match")
}

# Reorder df_inc columns to match df_exc
df_inc <- df_inc[ , names(df_exc)]

# Now names match exactly
identical(names(df_exc), names(df_inc))
```
```{r}
# Common columns
common <- intersect(names(df_exc), names(df_inc))

# Capture full class (handles cases like c("POSIXct","POSIXt"))
type_exc <- sapply(common, function(nm) paste(class(df_exc[[nm]]), collapse = "/"))
type_inc <- sapply(common, function(nm) paste(class(df_inc[[nm]]), collapse = "/"))

# Find and print mismatches only
mismatch <- type_exc != type_inc
out <- data.frame(
  column = common[mismatch],
  type_in_df_exc = type_exc[mismatch],
  type_in_df_inc = type_inc[mismatch],
  stringsAsFactors = FALSE
)

if (nrow(out)) {
  print(out, row.names = FALSE)
} else {
  cat("No type mismatches among common columns.\n")
}

```
```{r}
# Convert mismatched columns in df_exc to numeric
df_exc$duration        <- as.numeric(gsub(",", ".", 
                                          as.character(df_exc$duration)))
df_exc$likert_response <- as.numeric(gsub(",", ".", 
                                          as.character(df_exc$likert_response)))
df_exc$likert_rescaled <- as.numeric(gsub(",", ".", 
                                          as.character(df_exc$likert_rescaled)))

# Check the classes after conversion
sapply(df_exc[c("duration", "likert_response", "likert_rescaled")], class)
```

```{r}
df.data <- bind_rows(df_exc, df_inc)
# save as csv file
write.csv(df.data,
          "/Users/irmakergin/Desktop/supplamentary/data/df_semantic_merged.csv",
          row.names = FALSE)
```

Define list of participant id's
```{r}
# Define the list of participant IDs
participant_ids <- c("p_1","p_2","p_3","p_4","p_5","p_6","p_7","p_8","p_9",
                     "p_10","p_11","p_12","p_13","p_14","p_15","p_16","p_17",
                     "p_18","p_19","p_20","p_21","p_22","p_23","p_24","p_25",
                     "p_26","p_27","p_28","p_29","p_30")
```

## I. Semantic Similarity
### How many words did included participants write in their summaries on average?

```{r}
# select only included participants
exc_participant_ids <- c("p_2","p_6","p_12","p_16","p_20","p_23","p_26","p_27")
df.data_inc <- df.data %>%
  filter(!participant %in% exc_participant_ids)

# on average, across speech rates
df.data_inc <- df.data_inc %>%
  mutate(
    summary_text = textbox.text_corrected_manual,
    summary_text = ifelse(is.na(summary_text), "", summary_text),
    summary_text = stringr::str_squish(summary_text),
    word_count   = ifelse(summary_text == "", NA_integer_,
                          stringr::str_count(summary_text, "\\S+"))
  )
overall_avg_inc <- df.data_inc %>%
  summarise(
    mean_words = round(mean(word_count, na.rm = TRUE),2),
    n_summaries = round(sum(!is.na(word_count)),2),
    total_words = round(sum(word_count, na.rm = TRUE),2)
  )

overall_avg_inc
```

```{r}
# on average, per speech rate
by_rate_inc <- df.data_inc %>%
  group_by(speech_rate) %>%
  summarise(
    mean_words = round(mean(word_count, na.rm = TRUE),2),
    sd_words   = round(sd(word_count, na.rm = TRUE),2),
    n_summaries = round(sum(!is.na(word_count)),2),
    total_words = round(sum(word_count, na.rm = TRUE),2),
    .groups = "drop"
  ) %>%
  arrange(suppressWarnings(as.numeric(as.character(speech_rate))))

by_rate_inc
```
#### Excluded vs Included participants' word counts:

Excluded participants reported 14.13 words per summary on average, whereas
included participants reported 18.99.
For the slowest condition, excluded participants reported 19.35 words on avg,
included participants 26.15.
sr2: 17.60 vs 24.81
sr3: 14.41 vs 22.57
sr4: 7.47 vs 9.86
sr5: 4.42 vs 5.92

Which semantic similarity analysis explains comprehension better?

### Visualization
First, let's visualize all 3 to see if they show the same pattern:

```{r figure-size, fig.width=9, fig.height=5}

# GloVe - Written Summary
average_similarity_summary <- df.data %>%
  group_by(speech_rate) %>%
  summarise(
    average_similarity = mean(glove_sum_max_similarity_rescaled, na.rm = TRUE),
    sd = sd(glove_sum_max_similarity_rescaled, na.rm = TRUE),
    n = n(),
    se = sd / sqrt(n)  # standard error
  )


# GloVe - Heard Segment
average_similarity_text <- df.data %>%
  group_by(speech_rate) %>%
  summarise(
    average_similarity = mean(glove_text_average_max_similarity, na.rm = TRUE),
    sd = sd(glove_text_average_max_similarity, na.rm = TRUE),
    n = n(),
    se = sd / sqrt(n)  # standard error
  )

# BERT 
average_similarity_bert <- df.data %>%
  group_by(speech_rate) %>%
  summarise(
    average_similarity = mean(bert_cosine_similarity, na.rm = TRUE),
    sd = sd(bert_cosine_similarity, na.rm = TRUE),
    n = n(),
    se = sd / sqrt(n)  # standard error
  )


# Create the plots without x and y labels
plot_glove_summary <- ggplot(average_similarity_summary, aes(x = factor(speech_rate), 
                               y = average_similarity, 
                               fill = as.factor(speech_rate))) +
  geom_bar(stat = "identity", position = "dodge", width = 0.7, fill = "green3") +
  scale_x_discrete(labels = function(x) paste0("x ", x)) +
  labs(x = NULL, y= NULL, 
       title = "GloVe- Written Summary") +
  geom_text(aes(label = round(average_similarity, 2)), 
            vjust = -1, position = position_dodge(width = 0.7), size = 3) +
  geom_errorbar(aes(ymin = average_similarity - se, ymax = average_similarity + se), 
                width = 0, position = position_dodge(width = 0.7)) + 
  theme(axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        plot.title = element_text(size = 13, hjust = 0.5))

plot_glove_text <- ggplot(average_similarity_text, aes(x = factor(speech_rate), 
                               y = average_similarity, 
                               fill = as.factor(speech_rate))) +
  geom_bar(stat = "identity", position = "dodge", width = 0.7, fill = "darkseagreen2") +
  scale_x_discrete(labels = function(x) paste0("x ", x)) +
  labs(x = NULL, y = NULL, 
       title = "GloVe - Heard Segment") +
  geom_text(aes(label = round(average_similarity, 2)), 
            vjust = -1, position = position_dodge(width = 0.7), size = 3) +
  geom_errorbar(aes(ymin = average_similarity - se, ymax = average_similarity + se), 
                width = 0,position = position_dodge(width = 0.7)) +
  theme(plot.title = element_text(size = 13, hjust = 0.5))

# Adjust the plot for BERT without individual axis labels
plot_bert <- ggplot(average_similarity_bert, aes(x = factor(speech_rate), 
                               y = average_similarity, 
                               fill = as.factor(speech_rate))) +
  geom_bar(stat = "identity", position = "dodge", width = 0.7, fill = "darkseagreen3") +
  scale_x_discrete(labels = function(x) paste0("x ", x)) +
  labs(x = NULL, y = NULL, 
       title = "BERT") +
  geom_text(aes(label = round(average_similarity, 2)), 
            vjust = -1.2, position = position_dodge(width = 0.7), size = 3) +
  geom_errorbar(aes(ymin = average_similarity - se, ymax = average_similarity + se), 
                width = 0, position = position_dodge(width = 0.7)) +
  theme(plot.title = element_text(size = 13, hjust = 0.5))

#put them in a grid 
grid.arrange(
  arrangeGrob(
  plot_glove_summary,plot_glove_text, plot_bert, 
    ncol = 3,
    left = textGrob("Average Normalized Cosine Similarity Value", 
                    rot = 90, vjust = 0.5),
   bottom = textGrob("Speech Rate", 
                    rot = 0, vjust = 0.5)
  ) 
)
```
### Correlation

Do 3 different semantic similarity measures correlate with each other?
```{r}
# Subset the relevant columns
semantic_columns <- df.data[, c("bert_cosine_similarity", 
                                "glove_text_average_max_similarity", 
                                "glove_sum_max_similarity_rescaled")]

# Calculate the correlation matrix
correlation_matrix <- cor(semantic_columns, use = "complete.obs")

# Print 
print(correlation_matrix)

```
Test if any of these correlations are statistically significant:
```{r}
# Correlation test between BERT and GloVe- Heard Segment
test1 <- cor.test(df.data$bert_cosine_similarity, 
                  df.data$glove_text_average_max_similarity)

# Correlation test between BERT and GloVe- Written Summary
test2 <- cor.test(df.data$bert_cosine_similarity, 
                  df.data$glove_sum_max_similarity_rescaled)

# Correlation test between GloVe- Heard Segment & GloVe- Written Summary
test3 <- cor.test(df.data$glove_text_average_max_similarity,
                  df.data$glove_sum_max_similarity_rescaled)

print(test1)
print(test2)
print(test3)

```

### Comparison
Which semantic similarity analysis method explains the most varience in comprehension?

To see which if  semantic similarity scores explains variance in comprehension better than the others,we conducted a linear mixed model was conducted to predict the 10-Point Scale responses based on BERT, GloVe- Written Summary, and GloVe- Heard Segment. Random effects for digit span score and digit in noise score were included in the model.


```{r}
model_all<- lmer(likert_rescaled ~ 
                 bert_cosine_similarity +   glove_text_average_max_similarity +   
                   glove_sum_max_similarity_rescaled + 
                (1 | digit_span_score) + 
                (1 | digit_in_noise_score), data = df.data)
#model_compare <- anova(model_g1, model_all)
summary(model_all) 
```
All fixed effects are significant, as it was for just included participants. Glove- Written Summary has the highest t value and estimate as it was for just included and just excluded participants. Therefore, I will use/ report the GLoVe- written summary Segment for the rest of the analyses.   

### Speech Rate 
Are semantic similarity scores btw speech rates sig different from each other?

#### Glove- Written Summary
```{r}
semantic.anova <- aov(glove_sum_max_similarity_rescaled ~ speech_rate, data = df.data)
summary(semantic.anova)

pairwise_results <- df.data %>% pairwise_t_test(
    glove_sum_max_similarity_rescaled ~ speech_rate, pool.sd = FALSE,
    p.adjust.method = "bonferroni"
    )
pairwise_results
```
All significant except x1-x2 as it was for just included participants

#### Glove- Heard Segment
```{r}
semantic.anova2 <- aov(glove_text_average_max_similarity ~ speech_rate, 
                       data = df.data)
summary(semantic.anova2)

pairwise_results2 <- df.data %>% pairwise_t_test(
    glove_text_average_max_similarity ~ speech_rate, pool.sd = FALSE,
    p.adjust.method = "bonferroni"
    )
pairwise_results2
```
All significant except x1-x2, x2 & x3 aare significant unlike in just included 

#### BERT
```{r}
semantic.anova3 <- aov(bert_cosine_similarity ~ speech_rate, data = df.data)
summary(semantic.anova3)

pairwise_results3 <- df.data %>% pairwise_t_test(
    bert_cosine_similarity ~ speech_rate, pool.sd = FALSE,
    p.adjust.method = "bonferroni"
    )
pairwise_results3
```
inc + exc: included particiapants: All significant except x1-x2 & x2-x3
included particiapants: All significant except x2-x3

### Recency Effect
Is there a recency effect in summaries that participants wrote?

#### Glove- Written Summary
```{r}
# First, make sure that the right ones are NA, right now NAs are also 0
df.data <- df.data %>%
  mutate(
    rescaled_glove_bin1 = ifelse(textbox.text_corrected_manual == "", 
                                 NA, rescaled_glove_bin1),
    rescaled_glove_bin2 = ifelse(textbox.text_corrected_manual == "", 
                                 NA, rescaled_glove_bin2),
    rescaled_glove_bin3 = ifelse(textbox.text_corrected_manual == "", 
                                 NA, rescaled_glove_bin3),
    rescaled_glove_bin4 = ifelse(textbox.text_corrected_manual == "", 
                                 NA, rescaled_glove_bin4),
    rescaled_glove_bin5 = ifelse(textbox.text_corrected_manual == "", 
                                 NA, rescaled_glove_bin5)
  )

# Create a long dataset for bins and scores
df.bin <- df.data %>%
  select(participant, index, speech_rate, segment_text, textbox.text_corrected_manual, 
         glove_bin1, glove_bin2, glove_bin3, glove_bin4, glove_bin5) %>%
  pivot_longer(cols = starts_with("glove_bin"), 
               names_to = "bin", 
               names_prefix = "glove_bin", 
               values_to = "semantic_score") %>%
  mutate(bin = as.integer(bin)) %>%
  arrange(participant, index, bin)

# If a recency effect ->  latter bins should be recalled better than earlier ones
binned.anova <- aov(semantic_score ~ speech_rate * bin, data = df.bin)
summary(binned.anova)

df.bin_factor = df.bin %>%
  mutate(speech_bin = factor(paste(speech_rate, bin, sep="_")))

# pairwise comparison
df.bin_factor %>% pairwise_t_test(
   semantic_score ~ speech_bin, pool.sd = FALSE,
    p.adjust.method = "bonferroni"
    )
```

#### Glove- Heard Segment
```{r}
# First, make sure that the right ones are NA, right now NAs are also 0

df.data <- df.data %>%
  mutate(
    glove2_bin1 = ifelse(textbox.text_corrected_manual == "", NA, glove2_bin1),
    glove2_bin2 = ifelse(textbox.text_corrected_manual == "", NA, glove2_bin2),
    glove2_bin3 = ifelse(textbox.text_corrected_manual == "", NA, glove2_bin3),
    glove2_bin4 = ifelse(textbox.text_corrected_manual == "", NA, glove2_bin4),
    glove2_bin5 = ifelse(textbox.text_corrected_manual == "", NA, glove2_bin5)
  )

# Create a long dataset for bins and scores 
df.bin_glove2 <- df.data %>%
  select(participant, index, speech_rate, segment_text, textbox.text_corrected_manual, 
         glove2_bin1, glove2_bin2, glove2_bin3, glove2_bin4, glove2_bin5) %>%
  pivot_longer(cols = starts_with("glove2_bin"), 
               names_to = "bin", 
               names_prefix = "glove2_bin", 
               values_to = "glove2_score") %>%
  mutate(bin = as.integer(bin)) %>%
  arrange(participant, index, bin)

# If a recency effect ->  latter bins should be recalled better than earlier ones

binned.anova2 <- aov(glove2_score ~ speech_rate * bin, data = df.bin_glove2)
summary(binned.anova2)

df.bin_factor = df.bin_glove2 %>%
  mutate(speech_bin = factor(paste(speech_rate, bin, sep="_")))

# pairwise comparison
df.bin_factor %>% pairwise_t_test(
   glove2_score ~ speech_bin, pool.sd = FALSE,
    p.adjust.method = "bonferroni"
    )
```

#### BERT
```{r}
# Create a long dataset for bins and scores for BERT
df.bin_bert <- df.data %>%
  select(participant, index, speech_rate, segment_text, textbox.text_corrected_manual, 
         cosine_similarity_bin1, 
         cosine_similarity_bin2, 
         cosine_similarity_bin3, 
         cosine_similarity_bin4, 
         cosine_similarity_bin5) %>%
  pivot_longer(cols = starts_with("cosine_similarity_bin"), 
               names_to = "bin", 
               names_prefix = "cosine_similarity_bin", 
               values_to = "bert_score") %>%
  mutate(bin = as.integer(bin)) %>%
  arrange(participant, index, bin)

binned.anova_bert <- aov(bert_score ~ speech_rate * bin, data = df.bin_bert)
summary(binned.anova_bert)

df.bin_bert_factor = df.bin_bert %>%
  mutate(speech_bin = factor(paste(speech_rate, bin, sep="_")))

# pairwise comparison
df.bin_bert_factor %>% pairwise_t_test(
   bert_score ~ speech_bin, pool.sd = FALSE,
    p.adjust.method = "bonferroni"
    )
```

There is a main effect of Speech Rate for all 3, main effect of binning (recency) only for GloVe- Heard Summary & BERT, as it was for just included and just excluded.

## II. Validation
Can we predict the scores of our novel comprehension measure from the existing post-hoc comprehension measures?

### Each measure as a fixed effect in seperate models

#### 10-Point Scale Ratings

```{r}
# Calculate median trial movements for each trial

df.data <- df.data %>%
  mutate(
    slider_values_numeric = str_split(slider_values_rescaled, ",") %>%
      map(~ as.numeric(.x))
  )

# Mean and median slider values for each trial
df.data <- df.data %>%
  rowwise() %>%
  mutate(trial_mean_rescaled = mean(unlist(slider_values_numeric), na.rm = TRUE),
         trial_median_rescaled = median(unlist(slider_values_numeric), na.rm = TRUE)) %>%
  ungroup()
```

```{r}
model_likert<- lmer(trial_median_rescaled ~ 
                likert_rescaled + 
                (1 | digit_span_score) + 
                (1 | digit_in_noise_score), data = df.data)

summary(model_likert)
```
##### variance explained by the fixed effect (partial r2)
The proportion of variance explain uniquely by the predictor relative to total
variance
```{r}
res_likert <- partR2(model_likert, 
              partvars = "likert_rescaled", 
              data = df.data, 
              R2_type = "marginal")
res_likert

```
0.8% - partial R2= 0.78 


Cohen's f2
```{r}
 
mf <- model.frame(model_likert, na.action = na.omit)
model_clean <- lmer(formula(model_likert), data = mf, REML = lme4::isREML(model_likert))

## 1) Marginal R^2 and Cohen's f^2 (for the single fixed effect)
r2 <- r.squaredGLMM(model_clean)
R2_m <- as.numeric(r2[1])                 # fixed-effects R^2
f2   <- R2_m / (1 - R2_m)                 # Cohen's f^2

## 2) Partial R^2 for likert_rescaled
# With one fixed effect, partial R^2 == marginal R^2:
PR2_likert <- R2_m

## 3) Standardized coefficient (β): z-score both y and x
mf$y_z <- scale(mf$trial_median_rescaled)
mf$x_z <- scale(mf$likert_rescaled)
mod_std <- lmer(y_z ~ x_z + 
                  (1 | digit_span_score) + 
                  (1 | digit_in_noise_score),
                data = mf)
beta_std <- fixef(mod_std)["x_z"]

## Pretty print
cat(sprintf("Marginal R^2 (fixed effects): %.3f\n", R2_m))
cat(sprintf("Cohen's f^2: %.3f\n", f2))
cat(sprintf("Partial R^2 for likert_rescaled: %.3f\n", PR2_likert))
```


##### Visualize 10-Point Scale Ratings per Sepeech Speed
```{r figure-size, fig.width=6, fig.height=6 }

# Calculate the average 10-point scale scores per speech_rate category
average_score_likert <- df.data %>%
  group_by(speech_rate) %>%
  summarise(average_likert = mean(likert_rescaled, na.rm = TRUE),
            sd = sd(likert_rescaled, na.rm = TRUE),
            n = n(),
            se = sd / sqrt(n)  # standard error
  )

# Plot
likert_plot <- ggplot(average_score_likert, aes(x = factor(speech_rate), 
                                                y = average_likert)) +
  geom_bar(stat = "identity", width = 0.7, fill = "royalblue") +   
  labs(x = "Speech Rate", y = "10-Point Scale Response") +
  geom_text(aes(label = round(average_likert, 2)), vjust = -0.2, size = 6) +
  scale_x_discrete(labels = function(x) paste0("x ", x)) +
  geom_errorbar(aes(ymin = average_likert - se, ymax = average_likert + se), 
                width = 0, position = position_dodge(width = 0.5)) +  
  scale_y_continuous(breaks = c(0, 0.25, 0.50)) + 
  theme(axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24),
        axis.text.x = element_text(size = 20), 
        axis.text.y = element_text(size = 20))  

print(likert_plot)
```

#### Multiple Choice Quesitons
```{r}
model_multiple_choice<- lmer(trial_median_rescaled ~ 
                multiple_choice_accuracy + 
                (1 | digit_span_score) + 
                (1 | digit_in_noise_score), data = df.data)

summary(model_multiple_choice)
```
Nice, still significant! 

##### variance explained by the fixed effect (partial r2)
The proportion of variance explain uniquely by the predictor relative to total
variance
```{r}
res_mcq <- partR2(model_multiple_choice, 
              partvars = "multiple_choice_accuracy", 
              data = df.data, 
              R2_type = "marginal")
res_mcq

```
partial R2= 0.10

Cohen's f2
```{r}
## 1) Marginal R^2 (fixed effects) + Cohen's f^2
r2 <- r.squaredGLMM(model_multiple_choice)
R2_m <- as.numeric(r2[1])                # marginal R^2
f2   <- R2_m / (1 - R2_m)                # Cohen's f^2

## 2) Partial R^2 for the single fixed effect (equals marginal R^2)
PR2_mcq <- R2_m

## 3) Standardized beta (ΔSD_y per 1 SD_x)
df.data$y_z <- scale(df.data$trial_median_rescaled)
df.data$x_z <- scale(df.data$multiple_choice_accuracy)
mod_std <- lmer(y_z ~ x_z +
                  (1 | digit_span_score) +
                  (1 | digit_in_noise_score),
                data = df.data)
beta_std <- fixef(mod_std)["x_z"]

## 4) (Optional) Semi-standardized beta: SD(y) per 1 raw-unit of x
mod_semistd <- lmer(y_z ~ multiple_choice_accuracy +
                      (1 | digit_span_score) +
                      (1 | digit_in_noise_score),
                    data = df.data)
beta_semistd <- fixef(mod_semistd)["multiple_choice_accuracy"]

## Pretty print
cat(sprintf(
  "Marginal R^2: %.3f\nCohen's f^2: %.3f\nPartial R^2: %.3f",
  R2_m, f2, PR2_mcq
))
```

##### Visualize Multiple Choice Quesitons per Speech Rate
```{r figure-size, fig.width=6, fig.height=6 }
# Calculate the average multiple_choice_accuracy scores per speech_rate category
average_scores <- df.data %>%
  group_by(speech_rate) %>%
  summarise(average_accuracy = mean(multiple_choice_accuracy, na.rm = TRUE),
            sd = sd(multiple_choice_accuracy, na.rm = TRUE),
            n = n(),
            se = sd / sqrt(n)  # standard error
  )

question_plot <- ggplot(average_scores, aes(x = factor(speech_rate), y = average_accuracy)) +
  geom_bar(stat = "identity", width = 0.7, fill = "violetred") +   
  labs(x = "Speech Rate", y = "Multiple Choice Accuracy") +
  geom_text(aes(label = round(average_accuracy, 2)), vjust = -0.5, size = 6) +
  scale_x_discrete(labels = function(x) paste0("x ", x)) +
  geom_errorbar(aes(ymin = average_accuracy - se, ymax = average_accuracy + se), 
                width = 0, position = position_dodge(width = 0.5)) +
  # Add dashed line at chance level:
  geom_hline(yintercept = 0.25, linetype = "dashed", color = "black", size=1.5) +  
  scale_y_continuous(breaks = c(0, 0.25, 0.5)) +  
  theme(axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24),
        axis.text.x = element_text(size = 20),  
        axis.text.y = element_text(size = 20))  

print(question_plot)
```

#### Summary
```{r}
# Summary- GloVe- Written Summary
model_glove1<- lmer(trial_median_rescaled ~ 
                glove_sum_max_similarity_rescaled + 
                (1 | digit_span_score) + 
                (1 | digit_in_noise_score), data = df.data)

summary(model_glove1)
```
##### variance explained by the fixed effect (partial r2)
The proportion of variance explain uniquely by the predictor relative to total
variance
```{r}
res_sem <- partR2(model_glove1, 
              partvars = "glove_sum_max_similarity_rescaled", 
              data = df.data, 
              R2_type = "marginal")
res_sem

```
partial r2= 0.41


Cohen's f2
```{r}
## 1) Marginal R^2 (fixed effects) + Cohen's f^2
r2 <- r.squaredGLMM(model_glove1)
R2_m <- as.numeric(r2[1])                # marginal R^2
f2   <- R2_m / (1 - R2_m)                # Cohen's f^2

## 2) Partial R^2 (same as marginal R^2 with one fixed effect)
PR2_glove <- R2_m

## 3) Standardized beta (ΔSD_y per 1 SD_x)
df.data$y_glove_z <- scale(df.data$trial_median_rescaled)
df.data$x_glove_z <- scale(df.data$glove_sum_max_similarity_rescaled)
mod_std_glove <- lmer(y_glove_z ~ x_glove_z +
                        (1 | digit_span_score) +
                        (1 | digit_in_noise_score),
                      data = df.data)

## 4) (Optional) Semi-standardized beta: SD(y) per 1 raw-unit of glove predictor
mod_semistd_glove <- lmer(y_glove_z ~ glove_sum_max_similarity_rescaled +
                            (1 | digit_span_score) +
                            (1 | digit_in_noise_score),
                          data = df.data)

##  print
cat(sprintf(
  "Marginal R^2: %.3f\nCohen's f^2: %.3f\nPartial R^2: %.3f",
  R2_m, f2, PR2_glove
))

```

Note: Marginal vs Partial R2
Marginal: How much variance all fixed effects together explain in the mixed model 
(random‐effect held constant).
How much variance a single fixed effect uniquely explains beyond the other fixed 
effects, with the random structure held constant.
So with an only 1-fixed effect in the model marginal r2= partial r2

##### Visualize Semantic Simlarity Scores of Summaries per Speech Rate
```{r figure-size, fig.width=6, fig.height=6}
plot_glove_summary <- ggplot(average_similarity_summary, aes(x = factor(speech_rate), 
                               y = average_similarity, 
                               fill = as.factor(speech_rate))) +
  geom_bar(stat = "identity", position = "dodge", width = 0.7, fill = "green3") +
  scale_x_discrete(labels = function(x) paste0("x ", x)) +
  labs(x = "Speech Rate", y= "Semantic Similarity\nScore") +
  geom_text(aes(label = round(average_similarity, 2)), 
            vjust = -0.5, position = position_dodge(width = 0.7), size = 6) +
  geom_errorbar(aes(ymin = average_similarity - se, ymax = average_similarity + se), 
                width = 0, position = position_dodge(width = 0.7)) + 
  scale_y_continuous(breaks = c(0, 0.25, 0.5), limits = c(0, 0.5)) +  
  theme(axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24),
        axis.text.x = element_text(size = 20),  
        axis.text.y = element_text(size = 20), 
        plot.title = element_text(size = 20, hjust = 0.5))

plot_glove_summary
```

### Visualize single fixed effect regression models
```{r figure-size, fig.width=6, fig.height=6 }
visreg_summary <- visreg(model_glove1, "glove_sum_max_similarity_rescaled", gg=TRUE,    
                         line=list(col="green3", size=1.7), points=list(alpha=0.5),
                         xlab= "Semantic Similarity Score", 
                         ylab= "Predicted Real-Time\nComprehension Score") +
  theme(axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24),
        axis.text.x = element_text(size = 20),  # Adjust X-axis tick label size
        axis.text.y = element_text(size = 20)) +  # Adjust Y-axis tick label size
  scale_x_continuous(breaks = c(0, 0.5, 1)) +  # Set x-axis ticks at 0, 0.5, 1
  scale_y_continuous(breaks = c(0, 0.5, 1)) 


visreg_likert <- visreg(model_likert, "likert_rescaled", gg=TRUE,
                        line=list(col="royalblue",size=1.7), points=list(alpha=0.5),
                        xlab= "10-point Scale Response", 
                        ylab= "") +
theme(axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24),
        axis.text.x = element_text(size = 20),  # Adjust X-axis tick label size
        axis.text.y = element_text(size = 20)) +  # Adjust Y-axis tick label size
  scale_x_continuous(breaks = c(0, 0.5, 1)) +  # Force x-axis to include 0, 0.5, 1
  scale_y_continuous(breaks = c(0, 0.5, 1))


visreg_multiple <- visreg(model_multiple_choice, "multiple_choice_accuracy", gg=TRUE,
                          line=list(col="violetred", size=1.7), points=list(alpha=0.5),
                          xlab= "Multiple Choice Accuracy", 
                          ylab= "") +
  theme(axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24),
        axis.text.x = element_text(size = 20),  # Adjust X-axis tick label size
        axis.text.y = element_text(size = 20)) +  # Adjust Y-axis tick label size
  scale_x_continuous(breaks = c(0, 0.5, 1)) +  # Set x-axis ticks at 0, 0.5, 1
  scale_y_continuous(breaks = c(0, 0.5, 1))


visreg_summary
visreg_likert
visreg_multiple
```

### Visualize regression models + Bar plots 
```{r figure-size, fig.width=18, fig.height=14}
# Create a multi-panel plot for 

# Create title groups
title1 <- textGrob("Summary", gp=gpar(fontsize=28, color='green3',fontface="bold"))
title2 <- textGrob("10-Point Scale", gp=gpar(fontsize=28, color='royalblue', fontface="bold"))
title3 <- textGrob("Multiple Choice Question", gp=gpar(fontsize=28,color='violetred', fontface="bold"))

combined_plot_effects <- grid.arrange(
  title1, title2, title3,
  visreg_summary, visreg_likert, visreg_multiple,
  plot_glove_summary, likert_plot, question_plot,
  ncol = 3,
  nrow = 4,
  heights = unit.c(unit(4, "null"), unit(8, "null"), unit(2, "null"), unit(8, "null")),  # Adjust heights
  layout_matrix = rbind(c(1, 2, 3), c(4, 5, 6), c(NA, NA, NA), c(7, 8, 9))
)

print(combined_plot_effects)
```

## All post-hoc measures as fixed effects in one regression model
Now predict the novel measure's scores from all post-hoc comprehension measures to see if they can explain independent variance.

```{r}
model_all_glove1 <- lmer(trial_median_rescaled ~  
                glove_sum_max_similarity_rescaled +
                likert_rescaled + 
                multiple_choice_accuracy + 
                (1 | digit_span_score) + 
                (1 | digit_in_noise_score), data = df.data)

summary(model_all_glove1)
```
Same as just inc and just exc, multiple choice is now not significant

Correlation between predictors:
```{r}
cor(df.data[, c("glove_sum_max_similarity_rescaled", 
                "likert_rescaled", 
                "multiple_choice_accuracy")], use = "complete.obs")

```
##### variance explained
```{r}
library(lme4)
library(MuMIn)

cohens_f2_lmer <- function(mod, digits = 3) {
  stopifnot(inherits(mod, "lmerMod"))

  # Use the exact rows the model used (avoid NA mismatches)
  mf <- model.frame(mod, na.action = na.omit)
  mod_clean <- lmer(formula(mod), data = mf, REML = lme4::isREML(mod))

  # Pieces
  resp         <- as.character(formula(mod_clean))[2]
  fixed_terms  <- attr(terms(mod_clean), "term.labels")         # fixed-only labels
  rand_terms   <- lme4::findbars(formula(mod_clean))            # random terms

  # Keep random effects in all reduced models
  rand_str <- if (length(rand_terms)) {
    vapply(rand_terms, function(x) paste0("(", deparse(x), ")"), character(1))
  } else character(0)

  # Model-level R^2 (marginal for fixed effects)
  r2_full_vec <- r.squaredGLMM(mod_clean)
  r2_full_m   <- as.numeric(r2_full_vec[1])   # Marginal R^2 (fixed effects)
  r2_full_c   <- as.numeric(r2_full_vec[2])   # Conditional R^2 (fixed + random), FYI

  # Build reduced models dropping ONE fixed term at a time
  rows <- lapply(fixed_terms, function(trm) {
    keep_fixed <- setdiff(fixed_terms, trm)
    fixed_rhs  <- if (length(keep_fixed)) paste(keep_fixed, collapse = " + ") else "1"
    rhs        <- paste(c(fixed_rhs, rand_str), collapse = " + ")
    f_reduced  <- as.formula(paste(resp, "~", rhs))

    m_red   <- lmer(f_reduced, data = mf, REML = lme4::isREML(mod_clean))
    r2_red  <- as.numeric(r.squaredGLMM(m_red)[1])             # marginal R^2 of reduced
    dR2     <- r2_full_m - r2_red                              # unique/semi-partial R^2
    f2      <- if (is.finite(r2_full_m) && r2_full_m < 1) dR2 / (1 - r2_full_m) else NA_real_

    data.frame(
      Predictor     = trm,
      Marginal_R2   = r2_full_m,    # same for all rows (model-level)
      Partial_R2    = dR2,          # unique/semi-partial R^2 for this predictor
      R2_reduced    = r2_red,       # for transparency
      Cohen_f2      = f2,
      stringsAsFactors = FALSE
    )
  })

  out <- bind_rows(rows) |>
    arrange(desc(Partial_R2)) |>
    mutate(across(c(Marginal_R2, Partial_R2, R2_reduced, Cohen_f2),
                  ~ round(., digits)))

  # (optional) attach conditional R^2 as an attribute for reference
  attr(out, "R2_conditional_model") <- round(r2_full_c, digits)
  out
}

# ----- Use it -----
f2_tbl <- cohens_f2_lmer(model_all_glove1, digits = 3)
f2_tbl
# View the model Conditional R^2 (optional):
attr(f2_tbl, "R2_conditional_model")

# Cohen (1988) benchmarks: small ~0.02, medium ~0.15, large ~0.35
```

### Visualize the multiple fixed effects regression
```{r figure-size, fig.width=15, fig.height=5 }

visreg_summary_all <- visreg(model_all_glove1, "glove_sum_max_similarity_rescaled", 
                             gg=TRUE,
                          line=list(col="green3", size = 1.7), 
                          points=list(alpha=0.5),
                       xlab= "Semantic Similarity Score", 
                       ylab= "Predicted Real-Time\nComprehension Score") + 
  theme(axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24),
        axis.text.x = element_text(size = 20),  
        axis.text.y = element_text(size = 20)) +  
  scale_x_continuous(breaks = c(0, 0.5, 1)) +  
  scale_y_continuous(breaks = c(0, 0.5, 1))    

# Update for visreg_likert
visreg_likert_all <- visreg(model_all_glove1, "likert_rescaled", gg=TRUE,
                        line=list(col="royalblue",size=1.7), points=list(alpha=0.5),
                       xlab= "10-point Scale Response",
                       ylab= NULL)+ 
  theme(axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24),
        axis.text.x = element_text(size = 20),  
        axis.text.y = element_text(size = 20)) +  
  scale_x_continuous(breaks = c(0, 0.5, 1)) +  
  scale_y_continuous(breaks = c(0, 0.5, 1))    

# Update for visreg_multiple
visreg_multiple_all <- visreg(model_all_glove1, "multiple_choice_accuracy", gg=TRUE,
                           line=list(col="violetred", size=1.7), points=list(alpha=0.5),
                       xlab= "Multiple Choice Accuracy", 
                       ylab= NULL) +
  theme(axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24),
        axis.text.x = element_text(size = 20),  
        axis.text.y = element_text(size = 20)) +  
  scale_x_continuous(breaks = c(0, 0.5, 1)) +  
  scale_y_continuous(breaks = c(0, 0.5, 1))    

# Arrange plots in a grid
grid.arrange(
  arrangeGrob(
    visreg_summary_all, visreg_likert_all, visreg_multiple_all, 
    ncol = 3
  ) 
)


# For random slopes 
visreg_wm <- visreg(model_all_glove1, "digit_span_score", gg=TRUE,
                       xlab= "Working Memory Scores", 
                       ylab= NULL) 
  #scale_y_continuous(breaks = c(1, 2, 3, 4, 5), limits = c(1, 5))

visreg_hearing <- visreg(model_all_glove1, "digit_in_noise_score", gg=TRUE,
                       xlab= "Hearing In Noise", 
                       ylab= NULL)
  #scale_y_continuous(breaks = c(1, 2, 3, 4, 5), limits = c(1, 5))
  

# put them in a grid
grid.arrange(
  arrangeGrob(
   visreg_wm, visreg_hearing,
    ncol = 2,
    left = textGrob(" Predicted real-time comprehension scores 
                    given the post-hoc measures", 
                    rot = 90, vjust = 1.5)
  ) 
)
```

## Figure: Single fixed-effect regressions + bar plots + multiple fixed-effect regression
```{r figure-size, fig.width=18, fig.height=22}
# all 3 plots in the same grid
# Create title groups
title1 <- textGrob("Summary", gp=gpar(fontsize=28, 
                                      color='green3',
                                      fontface="bold"))
title2 <- textGrob("10-Point Scale", gp=gpar(fontsize=28, 
                                             color='royalblue', 
                                             fontface="bold"))
title3 <- textGrob("Multiple Choice Question", gp=gpar(fontsize=28,
                                                       color='violetred', 
                                                       fontface="bold"))

combined_plot_effects <- grid.arrange(
  title1, title2, title3,
  visreg_summary, visreg_likert, visreg_multiple,
  plot_glove_summary, likert_plot, question_plot,
  visreg_summary_all, visreg_likert_all, visreg_multiple_all,
  ncol = 3,
  nrow = 6,
  heights = unit.c(
    unit(4, "null"),  # Title row
    unit(8, "null"),  # First row of plots
    unit(2, "null"),  # Spacer row
    unit(8, "null"),  # Second row of plots
    unit(2, "null"),  # Spacer row (optional)
    unit(8, "null")   # Third row of plots
  ),
  layout_matrix = rbind(
    c(1, 2, 3),
    c(4, 5, 6),
    c(NA, NA, NA),
    c(7, 8, 9),
    c(NA, NA, NA),
    c(10, 11, 12)
  )
)


print(combined_plot_effects)
```
## Predicting real time comprehension from speech rate 
Does comprehension change with Speech Rate?

```{r}
model_rate <- lmer(speech_rate ~ 
                trial_median_rescaled +
                glove_sum_max_similarity_rescaled +
                likert_rescaled + 
                multiple_choice_accuracy + 
                (1 | digit_span_score) + 
                (1 | digit_in_noise_score), data = df.data)

summary(model_rate)
```

Multiple choice accuracy is not significant, like in just excluded participants,
unlike in just included participants.

Are the predictors (especially likert and real time comp) significantly 
different from each other?

```{r}

# select fixed effects in the model 
fe <- setdiff(names(fixef(model_rate)), "(Intercept)")
# pair each of them in combinations of 2
pairs <- t(combn(fe, 2))
# we will test the hypotheses b1=b2 (b1-b2=0) for each pair
# so we create the contrast matrix:
K <- t(apply(pairs, 1, function(p) {
  v <- setNames(numeric(length(fixef(model_rate))), names(fixef(model_rate)))
  v[p[1]] <-  1
  v[p[2]] <- -1
  v
}))
# name each row
rownames(K) <- apply(pairs, 1, function(p) paste(p[1], "=", p[2]))
# general linear hyp using the model (estimated coefficients and their covariance matrix) 
# and contrast matrix
gl <- glht(model_rate, linfct = K)
#test all contrasts with correction
summary(gl, test = adjusted("single-step"))

# Simultaneous 95% CIs
confint(gl, calpha = multcomp::adjusted_calpha())
```
yep, slider and likert responses are not significantly different from each other.


### Figure: Estimates of fixed effects (comprehension measures) on Speech Rate
```{r}
# Extract the fixed effects from the model (including confidence intervals)
fixed_effects <- tidy(model_rate, effects = "fixed", conf.int = TRUE)

# Filter out the intercept term
fixed_effects <- fixed_effects %>%
  filter(term != "(Intercept)")

# Map the actual terms to custom axis labels
term_mapping <- c(
  "multiple_choice_accuracy" = "Multiple Choice Question Accuracy",
  "glove_sum_max_similarity_rescaled" = "Summary Semantic Similarity",
  "likert_rescaled" = "10-Point Scale",
  "trial_median_rescaled" = "Median Real-Time Comprehension"
)

# Replace the term names with custom labels
fixed_effects <- fixed_effects %>%
  mutate(term = recode(term, !!!term_mapping))

# Reorder the terms based on the estimate values in descending order
fixed_effects <- fixed_effects %>%
  mutate(term = reorder(term, -estimate))

# Add a column for significance stars based on p-values
fixed_effects <- fixed_effects %>%
  mutate(sig_stars = case_when(
    p.value < 0.001 ~ "***",
    p.value < 0.01 ~ "**",
    p.value < 0.05 ~ "*",
    TRUE ~ ""
  ))

# Plot with ggplot2 - swapped x and y axes
ggplot(fixed_effects, aes(y = term, x = estimate)) +  # Swapped axes
  geom_point(aes(color = term), size = 3) +  # Add color to the points
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high, color = term), 
                 height = 0, 
                 width = 0) +  
  geom_text(aes(label = paste0(round(estimate, 2), sig_stars)), vjust = -1, size = 4) +  
  scale_color_manual(values = c(
    "Multiple Choice Question Accuracy" = "violetred",
    "10-Point Scale" = "royalblue",
    "Summary Semantic Similarity" = "green3",
    "Median Real-Time Comprehension" = "purple"
  )) + 
  labs(title = " ",
       x = "Regression Coefficient Estimates",
       y = NULL) +  
  theme(
    plot.title = element_text(hjust = 0.5, size = 18),  
    axis.title.x = element_text(size = 13),              
    axis.text.y = element_text(size = 13, color = "black"),  
    axis.text.x = element_text(size = 12) 
  ) + 
  guides(color = "none") 

```

#DEMOGRAPHICS

Excluded vs included participants:

##Excluded
Mean: 30.71
sd:8.12
median:27
range:23-47
gender:

##Included
Mean:23.26
sd:5.31
median:22
range:18-39



